### 2022-12-20 source/abstract.tex
R packages

Possible answers to this question are given in the first and largest part of
this thesis. It consists of three extensions to a recently proposed
reverse-Bayes method for quantifying replication success. The key idea of the
method is to challenge the data from the original study with a sceptical prior
distribution so that the resulting posterior distribution no longer indicates
evidence for an effect. The goal of the replication study is then to show that
the sceptical prior is unrealistic, and replication success is achieved if there
is sufficient conflict between the prior and the replication data. The procedure
can be summarized in a single quantitative measure, termed the sceptical
$p$-value.
% extension 1
The first extension recalibrates the sceptical $p$-value so that replication
success takes effect size more appropriately into account. Specifically, the
recalibration is chosen such that for original studies which were borderline
significant, replication success can only be achieved if the effect estimate
from the replication study is larger than the effect estimate from the original
study. We find that the recalibrated sceptical $p$-value also has good
frequentist properties comparable to the standard method used in practice.
% extension 2
The second extension replaces tail probabilities with Bayes factors as measures
of evidence. The procedure can again be summarized in a single measure called
the sceptical Bayes factor.
% The sceptical prior is now determined such that the original finding is no
% longer convincing in terms of a Bayes factor. In contrast to tail
% probabilities,
% We find that the extended method combines two notions of replicability: It
% requires that original and replication study independently provide evidence for
% an effect and ensures that their effect estimates are compatible.
The sceptical Bayes factor has similar properties as the sceptical $p$-value but
it avoids a statistical paradox which the sceptical $p$-value suffers from -- in
some situations the sceptical $p$-value may indicate replication success even
though the effect estimate from the replication is arbitrarily smaller than the
effect estimate from the original study. % , which cannot happen with the sceptical
% Bayes factor.
% Bayes factors have a more
% natural interpretation and allow for direct quantification of evidence for one
% hypothesis versus another. As with the sceptical $p$-value, the procedure leads
% to a single measure quantifying the degree of replication success called the
% sceptical Bayes factor.
The third extension provides a framework for Bayesian design of replication
studies which allows for combining data from the original study with external
knowledge. This approach can lead to potentially more efficient designs compared
to classical approaches, and it can be used for replication design based on both
the sceptical $p$-value and the sceptical Bayes factor.
% External knowledge, such as data from other studies, is ubiquitous in the
% replication setting and taking it into account can lead to potentially more
% efficient designs compared to classical approaches.

>>>>

Possible answers to this question are given in the first and largest part of
this thesis. It consists of three extensions to a recently proposed
reverse-Bayes method for quantifying replication success. The key idea of the
method is to challenge the data from the original study with a sceptical prior
distribution so that the resulting posterior distribution no longer indicates
evidence for an effect. The goal of the replication study is then to show that
the sceptical prior is unrealistic, and replication success is achieved if there
is sufficient conflict between the prior and the replication data. The procedure
can be summarized in a single quantitative measure, termed the sceptical
$p$-value.
% extension 1
The first extension recalibrates the sceptical $p$-value so that replication
success takes effect size more appropriately into account. Specifically, the
recalibration is chosen such that for original studies which were borderline
significant, replication success can only be achieved if the effect estimate
from the replication study is larger than the effect estimate from the original
study. We find that the recalibrated sceptical $p$-value also has good
frequentist properties comparable to the standard method used in practice.
% extension 2
The second extension replaces tail probabilities with Bayes factors as measures
of evidence. The procedure can again be summarized in a single measure called
the sceptical Bayes factor.
% The sceptical prior is now determined such that the original finding is no
% longer convincing in terms of a Bayes factor. In contrast to tail
% probabilities,
% We find that the extended method combines two notions of replicability: It
% requires that original and replication study independently provide evidence for
% an effect and ensures that their effect estimates are compatible.
The sceptical Bayes factor has similar properties as the sceptical $p$-value but
it avoids a statistical paradox which the sceptical $p$-value suffers from -- in
some situations the sceptical $p$-value may indicate replication success even
though the effect estimate from the replication is substantially smaller than
the effect estimate from the original study. % , which cannot happen with the sceptical
% Bayes factor.
% Bayes factors have a more
% natural interpretation and allow for direct quantification of evidence for one
% hypothesis versus another. As with the sceptical $p$-value, the procedure leads
% to a single measure quantifying the degree of replication success called the
% sceptical Bayes factor.
The third extension provides a framework for Bayesian design of replication
studies which allows for combining data from the original study with external
knowledge. This approach can lead to potentially more efficient designs compared
to classical approaches, and it can be used for replication design based on both
the sceptical $p$-value and the sceptical Bayes factor.
% External knowledge, such as data from other studies, is ubiquitous in the
% replication setting and taking it into account can lead to potentially more
% efficient designs compared to classical approaches.

### 2022-12-20 source/intro.Rnw
R packages

A replication study (or simply replication) involves repeating the original
study as closely as possible but with new subjects. If the replication yields
similar results to the original study, this increases our confidence in the
original finding. However, if the replication study yields conflicting results,
this lowers our confidence in the original finding. %  As such, replication studies
% are an essential part of the scientific method. They provide a means for
% substantiating genuine research findings and refuting findings which occurred
% merely by chance.
The concept of replicability has long been a central part of the scientific
method. For instance, \citet[p. 13]{Fisher1935} noted ``\textit{no isolated
  experiment, however significant in itself, can suffice for the experimental
  demonstration of any natural phenomenon}''. For this reason, ``successful''
replication is typically a requirement for acceptance of newly proposed
scientific theories (\eg{} a new physical model). Yet, replication studies are
not only important for researchers, but also for decision makers and the general
population, as the implementation of policies based on scientific findings may
also depend on whether these findings can be replicated. For instance, for a
drug to be approved to the market, the United States food and drug
administration requires ``\textit{at least two adequate and well-controlled
  studies, each convincing on its own, to establish effectiveness}'' \citep[p.
3]{FDA1998}. The results from replication studies may hence have real-world
consequences. It is therefore important that the methodological aspects of
replication studies, such as their statistical design and analysis, are well
understood.

@@

ggarrange(plotA, plotB, ncol = 2)
@
\caption{Yearly number of results for search term ``replication study'' on Web
  of Science (left), and number of results normalized by the number of results
  for the search term ``study'' (right). The search was conducted on 2 December
  2022.}
\label{fig:scholar}
\end{figure}

@@

plotB <- ggplot(data = rpcbWithoutNA, aes(x = smdo, y = smdr)) +
    geom_abline(intercept = 0, slope = 1, alpha = 0.3) +
    geom_hline(yintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_vline(xintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_point(aes(fill = rsig), shape = 21, show.legend = FALSE) +
    geom_rug(aes(color = rsig), size = 0.3, show.legend = FALSE) +
    labs(x = "Original effect estimate (SMD)",
         y = "Replication effect estimate (SMD)",
         fill = "") +
    coord_fixed(xlim = zoom, ylim = zoom) +
    scale_fill_manual(values = cols, labels = scales::parse_format()) +
    scale_color_manual(values = cols) +
    theme_bw() +
    theme(panel.grid = element_blank())
ggpubr::ggarrange(plotA, plotB, ncol = 2, align = "v")
@
\caption{Results for 132 effects from the ``Reproducibility Project: Cancer
  Biology'' \citep{Errington2021} for which effect estimates and standard errors
  are available on standardized mean difference (SMD) scale. The right plot
  shows a zoomed-in view of the dotted area in the left plot. The
  \textit{p}-values are recomputed using a normal approximation. Two study pairs
  with original effect estimate larger than 80 are not shown.}
\label{fig:rpcb}
\end{figure}

@@

Many consider the prior to be also the weak point of Bayesian inference since it
is unclear how it should be specified in the absence of external knowledge. The
\emph{reverse-Bayes} approach, first proposed by \citet{Good1950}, is one way of
dealing with this issue. The idea is to reverse Bayes' theorem as
\begin{align*}
  f(\theta) = f(\theta \given \text{data}) \times
  \frac{f(\text{data})}{f(\text{data} \given \theta)}
\end{align*}
and instead ``downdate'' a posterior with the observed data. So, in contrast to
the conventional ``forward-Bayes'' approach where we start with a prior, update
it with the data, and end up with a posterior, the reverse-Bayes approach starts
with the posterior and ends up with the prior. For example, the posterior may be
specified to indicate evidence for/against a particular hypothesis under
investigation. Reverse-Bayes inference then revolves around the question of
whether the resulting prior is plausible in light of external knowledge, and if
so, this indicates support for the specified posterior.

@@

zr <- tr/sr
c <- so^2/sr^2
ps <- pSceptical(zo = zo, zr = zr, c = c, alternative = "two.sided", type = "nominal")
psFormat <- pFormat(p = ps)
@
\subsubsection{The sceptical \textit{p}-value}
To remove the dependence on the level $\alpha$, \citet{Held2020} proposed to
determine the smallest level at which replication success can be established.
This level is called the \emph{sceptical $p$-value} $p_{\text{S}}$, and it is
available in closed-form
\begin{align}
  \label{eq:ps}
  p_{\text{S}}
  % = \inf_{\alpha \in (0, 1)} \left\{\alpha : p_{\text{Box}} \leq \alpha \right\}.
  = 2\left\{1 - \Phi(|z_{\text{S}}|)\right\}
\end{align}
where
\begin{align*}
  z_{\text{S}}^{2}
  = \begin{cases}
    z^{2}_{\text{H}}/2 & \text{for} ~ c = 1 \\
    \left\{\left[z_{\text{A}}^{2}\left\{z_{\text{A}}^{2} +
          z_{\text{H}}^{2}(c - 1)\right\}\right]^{1/2}
      - z_{\text{A}}^{2}\right\}/(c - 1)
    & \text{for} ~ c \neq 1
  \end{cases}
\end{align*}
with arithmetic mean $z_{\text{A}}^{2} = (z^{2}_{o} + z^{2}_{r})/2$ and harmonic
mean $z_{\text{H}}^{2} = 2/(1/z^{2}_{o} + 1/z^{2}_{r})$ of the squared
$z$-statistics, and variance ratio $c = \sigma^{2}_{o}/\sigma^{2}_{r}$.
Replication success at level $\alpha$ is then equivalent to
$p_{\text{S}} \leq \alpha$. For instance, the sceptical $p$-values of the three
replication studies in Figure~\ref{fig:RBillustration} are
$p_{\text{S}} = \Sexpr{psFormat[1]}$, $p_{\text{S}} = \Sexpr{psFormat[2]}$, and
$p_{\text{S}} = \Sexpr{psFormat[3]}$ (from left to right), so we can see that
the third replication is unsuccessful at level $\alpha = 5\%$ but successful at
level $\alpha = 10\%$. However, the sceptical $p$-value does not necessarily
have to be dichotomized in this manner, but can also be interpreted as a
quantitative measure of replication success; the smaller $p_{\text{S}}$, the
higher the degree of replication success.

The sceptical $p$-value has several interesting properties \citep[Section
3]{Held2020}: First, it is always larger than the maximum of the original and
replication $p$-values ($p_{\text{S}} > \max\{p_{o}, p_{r}\}$), meaning that
both $p$-values have to be smaller than $\alpha$ such that replication success
at level $\alpha$ is possible. The sceptical $p$-value hence requires
\emph{both} studies to be sufficiently convincing on their own (in terms of
their $p$-values), similar to the significance criterion for replication
success. Second, if the $p$-values $p_{o}$ and $p_{r}$ remain fixed but the
relative effect estimate \mbox{$d = \that_{r}/\that_{o}$} decreases towards
zero, the sceptical $p$-value increases, meaning that shrinkage of the
replication effect estimate is penalized ($p_{\text{S}} \uparrow 1$ as
$d \downarrow 0$ for fixed $p_{o}$ and $p_{r}$). The sceptical $p$-value thus
takes effect shrinkage into account, unlike the significance criterion which can
be achieved with any non-zero replication effect estimate $\that_{r}$ provided
the standard error $\sigma_{r}$ is small enough. This property is desirable in
the replication setting as a smaller replication effect estimate $\that_{r}$ may
not be practically relevant anymore, despite its statistical significance.

@@

In this article, we therefore look closer at the ``success region'' of the
sceptical $p$-value in terms of the relative effect estimate
$d = \that_{r}/\that_{o}$. This perspective leads to the proposal of a new
default level for thresholding the sceptical $p$-value called the \emph{golden
  level} $\alpha_{G}$ (named ``golden'' because the golden ratio appears in its
derivation). The golden level is defined through the property that for an
original study which was borderline significant ($p_{o} = \alpha$), replication
success based on $p_{\text{S}} \leq \alpha_{G}$ is only possible if the
replication effect estimate is at least as large as the original one
($d \geq 1$). For instance, for the one-sided significance level
$\alpha = \Sexpr{round(alpha*100, 1)}\%$, the corresponding two-sided golden
level is $\alpha_{G} = \Sexpr{round(alphaG*100, 1)}\%$. The behavior of the
golden level seems to align with common sense: for original studies which were
already convincing (in terms of their $p$-value) the effect estimate in the
replication study is allowed to shrink, to some extent, whereas for less
convincing original studies (those with $p$-values around the significance
level) shrinkage is more strongly penalized. We find that for replication
studies with equal or larger sample size than the original study, replication
success based on the golden level controls the type I error rate at the same
level as the standard significance criterion. Similarly, if the original study
was adequately powered, replication success based on the golden level has
comparable or improved ``project power''compared to the significance criterion
(project power is the probability of replication success conditional on a true
effect size based on original and replication study). Case studies from four
large-scale replication projects \citep{Opensc2015, Camerer2016, Camerer2018,
  Cova2018} illustrate the properties of the golden level. In most cases
conclusions agree with the significance criterion, but in the differing cases,
the golden level seems to produce more appropriate inferences as it takes into
account effect shrinkage. This extension is now implemented as the default
option in the R package \texttt{ReplicationSuccess}.

@@

The reverse-Bayes approach from \citet{Held2020} is based on challenging the
original study with a sceptical prior so there is no longer evidence for an
effect. Evidence is quantified in terms of credible intervals and tail
probabilities. However, there exist also other measures of evidence, and it has
been a matter of long debates which is the most appropriate \citep[see
\eg{}][]{Berger1987, Casella1987, Royall1997, Berger2003, Benjamin2017,
  Lakens2018, Amrhein2019b}. In this paper, we extend the reverse-Bayes
assessment of replication studies to use Bayes factors \citep{Good1958,
  Jeffreys1961} for quantifying evidence and prior-data
conflict. % Bayes factors are also
% used for prior-data conflict assessment as suggested by \citep{Box1980}.
Similar to the sceptical $p$-value, the procedure leads to a single measure for
quantifying replication success, \emph{the sceptical Bayes factor}. Systematic
comparisons show that the sceptical Bayes factor has similar properties as the
sceptical $p$-value %due to the reverse-Bayes approach underlying both methods
(\eg{} it penalizes shrinkage of the replication effect estimate and requires
compelling evidence from both studies in terms of $p$-values and Bayes factors,
respectively). However, it is also shown that the sceptical $p$-value suffers
from a certain type of ``shrinkage paradox'', which is avoided by the sceptical
Bayes factor; when the $p$-value from the original study goes to zero,
replication success based on the sceptical $p$-value can be achieved with any
arbitrarily small replication effect estimate, whereas replication success based
on the sceptical Bayes factor poses a finite limit on how much shrinkage is
allowed. Technically, the procedure is more involved and closed-form solutions
for the sceptical Bayes factor are only available in special
situations. % and in terms of the
% ``Lambert W function'' \citep{Corless1996}.
The method is illustrated on data from the ``Social Sciences Replication
Project'' \citep{Camerer2018}, and implemented in the R package
\texttt{BayesRep} (\url{https://gitlab.uzh.ch/samuel.pawel/BayesRep}).

@@

Shortly after the acceptance of Paper~\ref{PaperIV}, the article by
\citet{Sondhi2021} appeared. It proposed a novel reverse-Bayes method called
\emph{Bayesian Additional Evidence}, and we noted some flaws in the article.
This prompted us to write a commentary. We show that -- contrary to the
statement by Sondhi et al. -- there is a closed form solution for the key
quantity in their approach termed ``Bayesian Additional Evidence tipping
point''.
% The Bayesian Additional Evidence method provides an answer to the question
% ``What prior do I have to choose so that that my unconvincing data become
% convincing?''.
The method is also closely related to the Analysis of Credibility by
\citet{Matthews2018}. We investigate differences and similarities of the two
methods, concluding that the priors determined through the Bayesian Additional
Evidence method are of limited use due to their restrictive assumption of having
equal variance as the data.

@@

\phantomsection
\addcontentsline{toc}{section}{Data and software}
\section*{Data and software}
The CC-By 4.0 licensed data from the ``Reproducibility Project: Cancer Biology''
\citep{Errington2021} were downloaded from
\url{https://doi.org/10.17605/osf.io/e5nvr}. The relevant variables were then
extracted from the file ``\texttt{RP\_CB Final Analysis - Effect level
  data.csv}''. All analyses from this chapter were conducted in the R
programming language version \Sexpr{paste(version$major, version$minor, sep =
  ".")} \citep{R}. The packages \texttt{dplyr} \citep{Wickham2022},
\texttt{ggplot2} \citep{Wickham2016}, \texttt{knitr} \citep{Xie2022},
\texttt{ReplicationSuccess} \citep{Held2020}, \texttt{UpSetR}
\citep{Gehlenborg2019}, and \texttt{xtable} \citep{Dahl2019} were used. Code and
data to reproduce this thesis are available at
\url{https://github.com/SamCH93/thesis}. A snapshot of the git repository is
archived at \url{https://doi.org/10.5281/zenodo.XXXXXXX}.

>>>>

A replication study (or simply replication) involves repeating the original
study as closely as possible but with new subjects. If the replication yields
similar results to the original study, this increases our confidence in the
original finding. However, if the replication study yields conflicting results,
this lowers our confidence in the original finding. %  As such, replication studies
% are an essential part of the scientific method. They provide a means for
% substantiating genuine research findings and refuting findings which occurred
% merely by chance.
The concept of replicability has long been a cornerstone of the scientific
method. For instance, \citet[p. 13]{Fisher1935} noted ``\textit{no isolated
  experiment, however significant in itself, can suffice for the experimental
  demonstration of any natural phenomenon}''. For this reason, ``successful''
replication is typically a requirement for acceptance of newly proposed
scientific theories (\eg{} a new physical model). Yet, replication studies are
not only important for researchers, but also for decision makers and the general
population, as the implementation of policies based on scientific findings may
also depend on whether these findings can be replicated. For instance, for a
drug to be approved to the market, the United States food and drug
administration requires ``\textit{at least two adequate and well-controlled
  studies, each convincing on its own, to establish effectiveness}'' \citep[p.
3]{FDA1998}. The results from replication studies may hence have real-world
consequences. It is therefore important that the methodological aspects of
replication studies, such as their statistical design and analysis, are well
understood.

@@

grid.arrange(plotA, plotB, ncol = 2)
@
\caption{Yearly number of results for search term ``replication study'' on Web
  of Science (left), and number of results normalized by the number of results
  for the search term ``study'' (right). The search was conducted on 2 December
  2022.}
\label{fig:scholar}
\end{figure}

@@

plotB <- ggplot(data = rpcbWithoutNA, aes(x = smdo, y = smdr)) +
    geom_abline(intercept = 0, slope = 1, alpha = 0.3) +
    geom_hline(yintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_vline(xintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_point(aes(fill = rsig), shape = 21, show.legend = FALSE) +
    geom_rug(aes(color = rsig), size = 0.3, show.legend = FALSE) +
    labs(x = "Original effect estimate (SMD)",
         y = "Replication effect estimate (SMD)",
         fill = "") +
    coord_fixed(xlim = zoom, ylim = zoom) +
    scale_fill_manual(values = cols, labels = scales::parse_format()) +
    scale_color_manual(values = cols) +
    theme_bw() +
    theme(panel.grid = element_blank())
grid.arrange(plotA, plotB, ncol = 2)
@
\caption{Results for 132 effects from the ``Reproducibility Project: Cancer
  Biology'' \citep{Errington2021} for which effect estimates and standard errors
  are available on standardized mean difference (SMD) scale. The right plot
  shows a zoomed-in view of the dotted area in the left plot. The
  \textit{p}-values are recomputed using a normal approximation. Two study pairs
  with original effect estimate larger than 80 are not shown.}
\label{fig:rpcb}
\end{figure}

@@

Many consider the prior to be also the weak point of Bayesian inference since it
is unclear how it should be specified in the absence of external knowledge. The
\emph{reverse-Bayes} approach, first proposed by \citet{Good1950}, is one way of
dealing with this issue. The idea is to reverse Bayes' theorem as
\begin{align*}
  f(\theta) = f(\theta \given \text{data}) \times
  \frac{f(\text{data})}{f(\text{data} \given \theta)}
\end{align*}
and instead ``downdate'' a posterior with the observed data. So, in contrast to
the conventional ``forward-Bayes'' approach where we start with a prior, update
it with the data, and end up with a posterior, the reverse-Bayes approach starts
with the posterior and ends up with the prior. For example, the posterior may be
specified to indicate evidence for/against a particular hypothesis under
investigation. Reverse-Bayes inference then revolves around the question of
whether the resulting prior is plausible in light of external data/knowledge,
and if so, this indicates support for the specified posterior.

@@

zr <- tr/sr
c <- so^2/sr^2
ps <- pSceptical(zo = zo, zr = zr, c = c, alternative = "two.sided", type = "nominal")
psFormat <- pFormat(p = ps)
@
\subsubsection{The sceptical \textit{p}-value}
To remove the dependence on the level $\alpha$, \citet{Held2020} proposed to
determine the smallest level at which replication success can be established.
This level is called the \emph{sceptical $p$-value} $p_{\text{S}}$, and it is
available in closed-form
\begin{align}
  \label{eq:ps}
  p_{\text{S}}
  % = \inf_{\alpha \in (0, 1)} \left\{\alpha : p_{\text{Box}} \leq \alpha \right\}.
  = 2\left\{1 - \Phi(|z_{\text{S}}|)\right\}
\end{align}
where
\begin{align*}
  z_{\text{S}}^{2}
  = \begin{cases}
    z^{2}_{\text{H}}/2 & \text{for} ~ c = 1 \\
    \left\{\left[z_{\text{A}}^{2}\left\{z_{\text{A}}^{2} +
          z_{\text{H}}^{2}(c - 1)\right\}\right]^{1/2}
      - z_{\text{A}}^{2}\right\}/(c - 1)
    & \text{for} ~ c \neq 1
  \end{cases}
\end{align*}
with arithmetic mean $z_{\text{A}}^{2} = (z^{2}_{o} + z^{2}_{r})/2$ and harmonic
mean $z_{\text{H}}^{2} = 2/(1/z^{2}_{o} + 1/z^{2}_{r})$ of the squared
$z$-statistics, and variance ratio $c = \sigma^{2}_{o}/\sigma^{2}_{r}$. A
sceptical $p$-value $\ps \leq \alpha$ is then equivalent to replication success
at level $\alpha$. For instance, the sceptical $p$-values of the three
replication studies in Figure~\ref{fig:RBillustration} are
$p_{\text{S}} = \Sexpr{psFormat[1]}$, $p_{\text{S}} = \Sexpr{psFormat[2]}$, and
$p_{\text{S}} = \Sexpr{psFormat[3]}$ (from left to right), so we can see that
the third replication is unsuccessful at level $\alpha = 5\%$ but successful at
level $\alpha = 10\%$. However, the sceptical $p$-value does not necessarily
have to be dichotomized in this manner, but can also be interpreted as a
quantitative measure of replication success; the smaller $p_{\text{S}}$, the
higher the degree of replication success.

The sceptical $p$-value has several interesting properties \citep[Section
3]{Held2020}: First, it is always larger than the maximum of the original and
replication $p$-values ($p_{\text{S}} > \max\{p_{o}, p_{r}\}$), meaning that
both $p$-values have to be smaller than $\alpha$ such that replication success
at level $\alpha$ is possible. The sceptical $p$-value hence requires
\emph{both} studies to be sufficiently convincing (in terms of their
$p$-values), similar to the significance criterion for replication success.
Second, if the $p$-values $p_{o}$ and $p_{r}$ remain fixed but the relative
effect estimate \mbox{$d = \that_{r}/\that_{o}$} decreases towards zero, the
sceptical $p$-value increases, meaning that shrinkage of the replication effect
estimate is penalized ($p_{\text{S}} \uparrow 1$ as $d \downarrow 0$ for fixed
$p_{o}$ and $p_{r}$). The sceptical $p$-value thus takes effect shrinkage into
account, unlike the significance criterion which can be achieved with any
non-zero replication effect estimate $\that_{r}$ provided the standard error
$\sigma_{r}$ is small enough. This property is desirable in the replication
setting as a smaller replication effect estimate $\that_{r}$ may not be
practically relevant anymore, despite its statistical significance.

@@

In this article, we therefore look closer at the ``success region'' of the
sceptical $p$-value in terms of the relative effect estimate
$d = \that_{r}/\that_{o}$. This perspective leads to the proposal of a new
default level for thresholding the sceptical $p$-value called the \emph{golden
  level} $\alpha_{G}$ (named ``golden'' because the golden ratio appears in its
derivation). The golden level is defined through the property that for an
original study which was borderline significant ($p_{o} = \alpha$), replication
success based on $p_{\text{S}} \leq \alpha_{G}$ is only possible if the
replication effect estimate does not shrink compared to the original one
($d \geq 1$). For instance, for the one-sided significance level
$\alpha = \Sexpr{round(alpha*100, 1)}\%$, the corresponding two-sided golden
level is $\alpha_{G} = \Sexpr{round(alphaG*100, 1)}\%$. The behavior of the
golden level seems to align with common sense: for original studies which were
already convincing (in terms of their $p$-value) the effect estimate in the
replication study is allowed to shrink, to some extent, whereas for less
convincing original studies (those with $p$-values around the significance
level) shrinkage is more strongly penalized. We find that for replication
studies with equal or larger sample size than the original study, replication
success based on the golden level controls the type I error rate at the same
level as the standard significance criterion. Similarly, if the original study
was adequately powered, replication success based on the golden level has
comparable or improved ``project power''compared to the significance criterion
(project power is the probability of replication success conditional on a true
effect size based on original and replication study). Case studies from four
large-scale replication projects \citep{Opensc2015, Camerer2016, Camerer2018,
  Cova2018} illustrate the properties of the golden level. In most cases
conclusions agree with the significance criterion, but in the differing cases,
the golden level seems to produce more appropriate inferences as it takes into
account effect shrinkage. This extension is now implemented as the default
option in the R package \texttt{ReplicationSuccess}.

@@

The reverse-Bayes approach from \citet{Held2020} is based on challenging the
original study with a sceptical prior so there is no longer evidence for an
effect. Evidence is quantified in terms of credible intervals and tail
probabilities. However, there exist also other measures of evidence, and it has
been a matter of long debates which is the most appropriate \citep[see
\eg{}][]{Berger1987, Casella1987, Royall1997, Berger2003, Benjamin2017,
  Lakens2018, Amrhein2019b}. In this paper, we extend the reverse-Bayes
assessment of replication studies to use Bayes factors \citep{Good1958,
  Jeffreys1961} for quantifying evidence and prior-data conflict. Similar to the
sceptical $p$-value, the procedure leads to a single measure for quantifying
replication success, \emph{the sceptical Bayes factor}. Systematic comparisons
show that the sceptical Bayes factor has similar properties as the sceptical
$p$-value -- it penalizes shrinkage of the replication effect estimate and
requires compelling evidence from both studies (in terms Bayes factors).
However, it is also shown that the sceptical $p$-value suffers from a certain
type of ``shrinkage paradox'', which is avoided by the sceptical Bayes factor;
when the $p$-value from the original study goes to zero, replication success
based on the sceptical $p$-value can be achieved with any arbitrarily small
replication effect estimate, whereas replication success based on the sceptical
Bayes factor poses a finite limit on how much shrinkage is allowed. Technically,
the procedure is more involved and closed-form solutions for the sceptical Bayes
factor are only available in special situations. % and in terms of the
% ``Lambert W function'' \citep{Corless1996}.
The method is illustrated on data from the ``Social Sciences Replication
Project'' \citep{Camerer2018}, and implemented in the R package
\texttt{BayesRep} (\url{https://gitlab.uzh.ch/samuel.pawel/BayesRep}).

@@

Shortly after the acceptance of Paper~\ref{PaperIV}, the article by
\citet{Sondhi2021} appeared. It proposed a novel reverse-Bayes method called
\emph{Bayesian Additional Evidence}, and we noted some flaws in the article.
This prompted us to write a commentary. We show that -- contrary to the claim by
Sondhi et al. -- there is a closed form solution for the key quantity in their
approach termed ``Bayesian Additional Evidence tipping point''.
% The Bayesian Additional Evidence method provides an answer to the question
% ``What prior do I have to choose so that that my unconvincing data become
% convincing?''.
The method is also closely related to the Analysis of Credibility by
\citet{Matthews2018}. We investigate differences and similarities of the two
methods, concluding that the priors determined through the Bayesian Additional
Evidence method are of limited use due to their restrictive assumption of having
equal variance as the data.

@@

\phantomsection
\addcontentsline{toc}{section}{Data and software}
\section*{Data and software}
The CC-By 4.0 licensed data from the ``Reproducibility Project: Cancer Biology''
\citep{Errington2021} were downloaded from
\url{https://doi.org/10.17605/osf.io/e5nvr}. The relevant variables were then
extracted from the file ``\texttt{RP\_CB Final Analysis - Effect level
  data.csv}''. All analyses from this chapter were conducted in the R
programming language version \Sexpr{paste(version$major, version$minor, sep =
  ".")} \citep{R}. The packages \texttt{dplyr} \citep{Wickham2022},
\texttt{ggplot2} \citep{Wickham2016}, \texttt{gridExtra} \citep{Auguie2017},
\texttt{knitr} \citep{Xie2022}, \texttt{ReplicationSuccess} \citep{Held2020},
\texttt{scales} \citep{Wickham2022b}, \texttt{UpSetR} \citep{Gehlenborg2019},
and \texttt{xtable} \citep{Dahl2019} were used. Code and data to reproduce this
thesis are available at \url{https://github.com/SamCH93/thesis}. A snapshot of
the git repository is archived at \url{https://doi.org/10.5281/zenodo.XXXXXXX}.

### 2022-12-20 source/thesis.Rnw
R packages

## Packages
library(ggplot2) # plotting
library(ggpubr) # combining ggplots
library(scales) # scales for plots
library(xtable) # table
library(ReplicationSuccess) # replication study stuff
library(dplyr) # data manipulation
library(UpSetR) # upset plot

>>>>

## Packages
library(ggplot2) # plotting
library(gridExtra) # combining ggplots
library(scales) # scales for plots
library(xtable) # table
library(ReplicationSuccess) # replication study stuff
library(dplyr) # data manipulation
library(UpSetR) # upset plot
